### 2022-04-25 paper/Chapters/Evaluation.tex
Add summaries

In order to evaluate the performance of the forked version of Moonlight developed for this paper, it must be tested against the other existing solutions.
The testing methodology employed to ensure the accuracy of the testing is described in Section \ref{sec:TestingMethodology}.
Then, the responsivity and latency of each solution is evaluated in Section \ref{sec:ResponsivityLatency}, and the quality of each solution's stream is evaluated in Section \ref{sec:Quality}.
Then, the forked version of Moonlight is evaluated in real world scenarios in Section \ref{sec:RealWorldTesting}.
Finally, the results are summarized and verdicts on each of the solutions' applicability to the research questions will be presented in Section \ref{sec:EvaluationSummary}.

>>>>

In order to evaluate the performance of the forked version of Moonlight developed for this paper, it must be tested against the other existing solutions.
The testing methodology employed to ensure the accuracy of the testing is described in Section \ref{sec:TestingMethodology}.
Then, the responsivity and latency of each solution is evaluated in Section \ref{sec:ResponsivityAndLatency}, and the quality of each solution's stream is evaluated in Section \ref{sec:Quality}.
Then, the forked version of Moonlight is evaluated in real world scenarios in Section \ref{sec:RealWorldTesting}.
Finally, the results are summarized and verdicts on each of the solutions' applicability to the research questions will be presented in Section \ref{sec:EvaluationSummary}.

### 2022-04-25 paper/Chapters/Hardware.tex
Add summaries

There are a lot of factors that go into designing and building an electrical system that fits the needs for this project.
This process begins by outlining the requirements in Section \ref{sec:HardwareRequirements}, followed by describing the process and methodology of choosing parts in Section \ref{sec:ChoosingParts}.
Then, the feasibility of prototyping such as system is discussed in Section \ref{sec:Prototyping}, and finally the system is designed and manufactured in Sections \ref{sec:DesigningThePCB} and \ref{sec:ManufacturingThePCB} respectively.

@@

\begin{figure}[b]
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.8\linewidth]{Figures/kicad/QFN-20-1EP_4x4mm}
    \caption{\emph{QFN-20-1EP\_4x4mm}}
    \label{fig:FootprintQFN204x4_Original}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.8\linewidth]{Figures/kicad/QFN-20-1EP_4x4mm_RevA}
    \caption{\emph{QFN-20-1EP\_4x4mm\_RevA}}
    \label{fig:FootprintQFN204x4_RevA}
  \end{subfigure}
  \caption[Two versions of the QFN-20-1EP\_4x4mm package]{The two footprints for components with the \emph{QFN-20-1EP\_4x4mm} package. The original footprint is shown in Figure \ref{fig:FootprintQFN204x4_Original}, while the revised footprint is shown in Figure \ref{fig:FootprintQFN204x4_RevA}}
  \label{fig:FootprintQFN204x4}
\end{figure}

@@

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/pcb/crops/final}
  \caption[Assembled PCB]{The assembled PCB}
  \label{fig:AssembledPCB}
\end{figure}

@@

>>>>

As discussed in Chapter \ref{Chapter2}, there currently is no commercial solution for a cheap, portable device that can leverage the power of a remote computer; hence, this thesis will investigate the development of such a solution.
There are a lot of factors that go into designing and building an electrical system that fits the needs for this project.
This process begins by outlining the requirements in Section \ref{sec:HardwareRequirements}, followed by describing the process and methodology of choosing parts in Section \ref{sec:ChoosingParts}.
Then, the feasibility of prototyping such as system is discussed in Section \ref{sec:Prototyping}, and finally the system is designed and manufactured in Sections \ref{sec:DesigningThePCB} and \ref{sec:ManufacturingThePCB} respectively.

@@

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.8\linewidth]{Figures/kicad/QFN-20-1EP_4x4mm}
    \caption{\emph{QFN-20-1EP\_4x4mm}}
    \label{fig:FootprintQFN204x4_Original}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.8\linewidth]{Figures/kicad/QFN-20-1EP_4x4mm_RevA}
    \caption{\emph{QFN-20-1EP\_4x4mm\_RevA}}
    \label{fig:FootprintQFN204x4_RevA}
  \end{subfigure}
  \caption[Two versions of the QFN-20-1EP\_4x4mm package]{The two footprints for components with the \emph{QFN-20-1EP\_4x4mm} package. The original footprint is shown in Figure \ref{fig:FootprintQFN204x4_Original}, while the revised footprint is shown in Figure \ref{fig:FootprintQFN204x4_RevA}}
  \label{fig:FootprintQFN204x4}
\end{figure}

@@

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/pcb/crops/final}
  \caption[Assembled PCB]{The assembled PCB}
  \label{fig:AssembledPCB}
\end{figure}

@@

\section{Summary}\label{sec:HardwareSummary}

In order to produce a hardware device capable of fitting the needs of the project, a careful balance between power and cost had to be found.
The Raspberry Pi Compute Module 4 offered enough power to power the project while maintaining a low cost and slim profile that enabled it to fit in a small mobile device.
One the CM4 was chosen, a custom PCB had to be designed and manufactured to tailor the Compute module to the needs of the project.
This included choosing compatible electronic components, designing a board that provided the necessary functionality, and developing multiple iterations of the board to fix problems as they arose.
